---
title: "Reproducible Publication Template"
output: html_document
runtime: shiny
---

# Interactive Notebook Template

## Motivation

Why not just make a Shiny app? This way, you can interweave your code cells with markdown to provide an explanation of what you're doing for your user. Additionally, you can leave in the code cells for instructional purposes.

## Variables

### Number of Bins

This variable is what determines how many bins there are. The bounds of each bin are automatically calculated.

```{r}
#| context: server
selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20)
```

### Bandwidth 

When we change the number of bins, the graph is automatically updated.
We can also change the bandwidth, which will update the best fitting curve.

```{r}
sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
```


## Graph

```{r}
renderPlot({
  hist(faithful$eruptions, probability = TRUE,
       breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)",
       main = "Geyser eruption duration")

  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```