---
title: "Reproducible Publication Template"
format: html
---

```{r}
#| code-fold: false
#| include: false
```

> Abstract: Please include the same abstract you used to submit your notebook to EasyChair. This template serves only as a guide. The only required sections are indicated as such. Please **DO NOT include authors** in your submission, as we have a blind review process.


## Purpose

Provide some information about your intended reader, what they will learn from your publication, and what background they need to get the most out of it.


## Methodology

Quickly describe assumptions and processing steps. Include URLs as necessary.

Most cells in this notebook are markdown cells. They describe the expected content of the notebook, steps for formatting and submitting notebooks, and relevant technologies. The proposed structure and procedures are based on community input and literature (see References)

You can use this template as a visual guide, or configure your Jupyter installation such that every notebook opens with this template, in either short of long version. To enable opening notebooks with this template, see instructions for using the Template nbextension, in the Data Processing section.

## Setup

### Library import

Import all the required Python libraries.

The code cell below is an example. When submitting your notebook, make sure that all external libraries are included in the requirements or environment file and library versions are explictly defined.

It is a good practice to organize the imported libraries by functionality, as shown below.

```{r}
#| label: load-packages

library(ggplot2)
```


## Parameter definitions

Set all relevant parameters for the notebook. By convention, parameters are uppercase, while all the other variables follow Python's guidelines.
Data import

Retrieve all the required data for the analysis. Include brief data descriptions, and DOIs where possible.

Please import data in one of two ways:

1. Reference data that is available online and continuously managed (preferred).
2. If the data is relatively small, please include the files along with the notebook. If you deal with large data, include a subset.


## Data processing and analysis

The core of the notebook is here. Split this section into subsections as required, and explain processing and analysis steps.

```{r}
#| label: scatterplot

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()
```


## Results

Describe and comment on the most important results. Include images and URLs as necessary.

This template presents the general structure of notebooks expected by EarthCube, along with recommendations for additional resources to be created to ensure that the notebook is easy to re-use.


## Future work

State suggested next steps, based on results obtained in this notebook. This section is optional.



## Funding

Include references to awards that supported this research. Add as many award references as you need.

- Award1 = {"agency": "US National Science Foundation", "award_code": "1928208", "award_URL": "https://www.nsf.gov/awardsearch/showAward?AWD_ID=1928208%22%7D
- Award2 = {"agency": "agency", "award_code": "award_code", "award_URL": "award_URL"}
- Award3 = ...


## Acknowledgements

Include any relevant acknowledgements, apart from funding (which was in section 1.6)

This notebook template extends the Earthcube template, which is a result of collaboration between the TAC Working Group and the EarthCube Office.

The template is licensed under a Creative Commons Attribution 4.0 International License.


## References

List relevant references.

1. Notebook sharing guidelines from reproducible-science-curriculum: https://reproducible-science-curriculum.github.io/publication-RR-Jupyter/
2. Guide for developing shareable notebooks by Kevin Coakley, SDSC: https://github.com/kevincoakley/sharing-jupyter-notebooks/raw/master/Jupyter-Notebooks-Sharing-Recommendations.pdf
3. Guide for sharing notebooks by Andrea Zonca, SDSC: https://zonca.dev/2020/09/how-to-share-jupyter-notebooks.html
4. Jupyter Notebook Best Practices: https://towardsdatascience.com/jupyter-notebook-best-practices-f430a6ba8c69
5. Introduction to Jupyter templates nbextension: https://towardsdatascience.com/stop-copy-pasting-notebooks-embrace-jupyter-templates-6bd7b6c00b94
    5.1. Table of Contents (Toc2) readthedocs: https://jupyter-contrib-nbextensions.readthedocs.io/en/latest/nbextensions/toc2/README.html
    5.2. Steps to install toc2: https://stackoverflow.com/questions/23435723/installing-ipython-notebook-table-of-contents
6. Rule A, Birmingham A, Zuniga C, Altintas I, Huang SC, et al. (2019) Ten simple rules for writing and sharing computational analyses in Jupyter Notebooks. PLOS Computational Biology 15(7): e1007007. https://doi.org/10.1371/journal.pcbi.1007007. Supplementary materials: example notebooks (https://github.com/jupyter-guide/ten-rules-jupyter) and tutorial (https://github.com/ISMB-ECCB-2019-Tutorial-AM4/reproducible-computational-workflows)
7. Languages supported by Jupyter kernels: https://github.com/jupyter/jupyter/wiki/Jupyter-kernels
8. EarthCube notebooks presented at EC Annual Meeting 2020: https://www.earthcube.org/notebooks
9. Manage your Python Virtual Environment with Conda: https://towardsdatascience.com/manage-your-python-virtual-environment-with-conda-a0d2934d5195
10. Venv - Creation of Virtual Environments: https://docs.python.org/3/library/venv.html


